\begin{center}
{\bf ACKNOWLEDGEMENTS}
\end{center}
I want to express my deep gratitude to all those people without whom this project would have never been completed. I want to give special appreciation to my supervisor, Dr. Prolay Kr. Mal, to provide me with the opportunity to work in CMS with this exciting work. Also, I want to thank my supervisor for his enthusiasm, support, encouragement, and patience, which help me to complete this project.\\
I would also like to thank my committee members: Prof. Sanjay Kr. Swain, Dr.Subhasis Basak, Dr. Yogesh K. Srivastava, and Dr. Amaresh K. Jaiswal for their comments and suggestions.\\
Furthermore, I would like to express special gratitude to Prafulla Saha; this work remains incomplete without his assistance. I also want to thank Alok Kumar Das, Amit Pal, Chandiprasad Kar, Kuldeep Kumar Pal, Lipsa Rani Panda, Priyanka Sadangi, Tribeni Mishra, and other lab members for their assistance and a healthy discussion over the doubts in the course of this project. Throughout this project, these people help me clarify the problem and make it simpler for me to understand the reasoning behind the processes. I also want to thank Er. Deepak Kr. Pattanaik for making the humorous, light, and wonderful environment in the lab.\\ 
 I want to thank DAE(India) for providing financial support. I also like to express my gratitude to the NISER and SPS, where I learned to develop a research career.\\
I also want to thank my mother, family, and friends for their patience and sacrifices during all this time.


 \begin{flushright}
 Shivam Raj 
 \end{flushright}                   


                                           

